\myTitle

### 2024-04-15 body-text-of-paper.tex
Small edits Tim had for us in Monday meeting!

A best practice for evaluating the behavior of genetic clustering algorithms on an empirical dataset is to conduct
parallel analyses on data that have been simulated---so the truth is known---so as to mirror the empirical data set
as closely as possible \citep{vaha2006efficiency,anderson2008improved,latch2011fine}.
Techniques to simulate individual genotypes in this context frequently use sampling with replacement from the
observed allele frequencies (see, for example, \citealt{nielsen2006hybridlab,kinziger2008hybridization}).
However, sampling with replacement implicitly increases the pairwise genetic distance among simulated samples, relative to the observed
samples, and
inflates the perceived statistical power to correctly assign individuals (or segments of the genome) back to source populations.
We refer to this phenomenon as resampling-induced, spurious power inflation (RISPI).
\citet{anderson2008improved} used simulations to document this type of artifact in the context of
genetic stock identification (GSI), a type of clustering application in which individuals are constrained to have
all their ancestry from a single subpopulation.
Similar statistical artifacts occur when simulating data to
assess how accurately admixture fractions can be estimated.

Beyond simply evaluating the resolution of discrete populations in a simulated framework, researchers may also be
interested in how individuals of admixed ancestry are genetically characterized given the statistical power of the available dataset and the
analysis methods used.
Recognizing that connectivity among genetically distinct populations may be relatively rare, additional insight into the
frequency of immigration can be gained by integrating across generations to identify both direct migrants and descendants of migrants
 (i.e., F1 hybrids or advanced hybrids reflecting the effect of backcrossing across multiple generations $[BC_1, \ldots,
BC_X])$.
Evaluating the results of genetic clustering algorithms in the context of data that are
expected to arrive by such a process of hybridization requires simulation of
explicit hybrids.  Such simulations are the purpose of the software {\sc hybridlab} 
\citep{nielsen2006hybridlab}.

@@

In this case,
each set of $N$ individuals is a sample from exactly the same population, so
there is clearly no basis for performing population assignment between $A$ and $B$;
however, we treated samples $A$ and $B$ as if they were sampled from two potentially different
populations, and simulated $9n$ new individuals: $n$ new individuals at each of the 9 values of
$q_A$, the admixture fraction for population $A$, in  $\{0, \frac{1}{8}, \frac{1}{4}, \frac{3}{8}, \frac{1}{2}, \frac{5}{8}, \frac{3}{4}, \frac{7}{8}, 1\}$.
We simulated these genotypes according to the "admixture model" used in {\em structure} \citep{pritchard2000inference}.  Briefly, at each
locus, independently, the origin
of each gene copy was simulated to be from
population $A$ with probability $q_A$ and from population $B$ with probability $1-q_A$.  Subsequently,
the allelic types of gene copies from $A$ ($B$), at a locus, were simulated by sampling with replacement
from the alleles at that locus in sample $A$ ($B$).
We then added these $9n$ simulated individuals to the $N$ original individuals  from $A$ and $N$ from $B$
and analyzed all the genotypes using ADMIXTURE with $K=2$. On each data set we performed a supervised analysis in which the original
$N$ samples from each
population were provided as learning samples, and also an
unsupervised analysis when the origin of the samples from $A$ and $B$ were regarded as unknown.

@@

Our approach for simulating admixed individuals without creating RISPI is motivated by the traditional cross-validation
approach for evaluating the power of mixture proportion
estimation in genetic stock identification (e.g., the cross-validation approach
described in \citealt{moran2019bayesian}).
In the cross-validation approach, individuals are removed from the reference
samples and placed in a mixture sample of "unknowns", whose origin
is inferred using the remaining individuals in the reference samples.  A key
feature of this approach is that no new genetic material is being created by
sampling with replacement; rather the genetic material of all individuals
in the original sample is being used---either within the remaining individuals in the
reference samples or within the individuals in the mixture.

>>>>

A best practice for evaluating the behavior of genetic clustering algorithms on empirical data is to conduct
parallel analyses on simulated data that mirror the empirical data set
as closely as possible \citep{vaha2006efficiency,anderson2008improved,latch2011fine} while providing
the benefit of known parameters (e.g.~$F_\mathrm{ST}$, admixture fractions, etc.) that can
be compared to estimates.
Techniques to simulate individual genotypes in this context frequently use sampling with replacement from the
observed allele frequencies (see, for example, \citealt{nielsen2006hybridlab,kinziger2008hybridization}).
However, sampling with replacement implicitly increases the pairwise genetic distance among simulated samples, relative to the observed
samples, and
inflates the perceived statistical power to correctly assign individuals (or segments of the genome) back to source populations.
We refer to this phenomenon as resampling-induced, spurious power inflation (RISPI).
\citet{anderson2008improved} used simulations to document this type of artifact in the context of
genetic stock identification (GSI), a type of clustering application in which individuals are constrained to have
all their ancestry from a single subpopulation.
Similar statistical artifacts occur when simulating data to
assess how accurately admixture fractions can be estimated.

Beyond simply evaluating the resolution of discrete populations in a simulated framework, researchers may also be
interested in how individuals of admixed ancestry are genetically characterized given the statistical power of the available dataset and the
analysis methods used.
Recognizing that connectivity among genetically distinct populations may be relatively rare, additional insight into the
frequency of immigration can be gained by integrating across generations to identify both direct migrants and descendants of migrants
 (i.e., F1 hybrids or advanced hybrids reflecting the effect of backcrossing across multiple generations $[BC_1, \ldots,
BC_X])$.
Evaluating the results and resolution of genetic clustering algorithms in the context of data that are
expected to arrive by such a process of hybridization requires simulation of
explicit hybrids.  Such simulations are the purpose of the software {\sc hybridlab} 
\citep{nielsen2006hybridlab}.

@@

In this case,
each set of $N$ individuals is a sample from exactly the same population, so
there is clearly no basis for performing population assignment between $A$ and $B$;
however, we treated samples $A$ and $B$ as if they were sampled from two potentially different
populations, and simulated $9n$ new individuals: $n$ new individuals at each of the 9 values of
$q_A$, the admixture fraction for population $A$, in  $\{0, \frac{1}{8}, \frac{1}{4}, \frac{3}{8}, \frac{1}{2}, \frac{5}{8}, \frac{3}{4}, \frac{7}{8}, 1\}$.
We simulated these genotypes according to the "admixture model" used in {\em structure} \citep{pritchard2000inference}.  Briefly, at each
locus, independently, the origin
of each gene copy was simulated to be from
population $A$ with probability $q_A$ and from population $B$ with probability $1-q_A$.  Subsequently,
the allelic types of gene copies from $A$ ($B$), at a locus, were simulated by sampling with replacement
from the alleles at that locus in sample $A$ ($B$).
We then analyzed all the genotypes ($9n + N + N$) using ADMIXTURE with $K=2$. On each data set we performed a supervised analysis in which the original
$N$ samples from each
population were provided as learning samples, and also an
unsupervised analysis when the origin of the samples from $A$ and $B$ were regarded as unknown.

@@

Our approach for simulating admixed individuals without creating RISPI is motivated by the traditional cross-validation
approach for assessing the power of mixed stock analysis (e.g., the ``Monte Carlo cross-validation'' approach
described in \citealt{moran2019bayesian}, p.~555).
In the cross-validation approach, individuals are removed from the reference
samples and placed in a mixture sample of ``unknowns,'' whose origin
is inferred using the remaining individuals in the reference samples.  A key
feature of this approach is that no new genetic material is being created by
sampling with replacement; rather the genetic material of all individuals
in the original sample is being used---either within the remaining individuals in the
reference samples or within the individuals set aside as a test set in the
simulated mixture.
